Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2023-05-31 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
update table 1 and 2 tables in appendix
Please just refer to changes in tables, other changes i did was to solve running problems

To explore the missingness, it is wise to look at the missing data pattern. The ten most frequent missingness patterns are shown:
```{r pattern, fig.height=7.1}
plot_pattern(dat, rotate = TRUE, npat = 10L)  # plot missingness pattern
```

>>>>

To explore the missingness, it is wise to look at the missing data pattern. The ten most frequent missingness patterns are shown:
```{r pattern, fig.height=7.1}
plot_pattern(dat, rotate = TRUE)  # plot missingness pattern
```
